Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-03-22 Journal1/Response1/Response.tex

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent  Comments to the Author} ``The paper has gone through three independent reviews and also checked by myself. The topic is interesting and there are merits. But there are some major concerns on the contribution, the assumption, the model derivation, and the experimental results. I hope the review comments are useful for further improving the quality of the paper. I'd therefore recommend the Resubmission''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. By utilizing the comments, we enhanced our paper and eliminated problems.

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem. The results seem promising but the paper has some issues. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for this manuscript's careful and thorough reading. We hope that the responses provided will ease the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text. A proofread is required before it can be accepted for publication.   ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
According to this comment, we have modified the introduction and checked the entire text and correct mistakes. We have shortened the state of the arts and introduced our goal briefly before the main contribution section. We removed additional information and talked more about our work. Also, we add some figures to describe incomprehensible parts. In addition, we provide further explanations.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Although the paper demonstrates its claims, the relaxation of conditions from the original problem formulation is not well justified. It is not clear why the initial formulation of the problem is not feasible and the reformulated makes it feasible while retaining some level of quality of the solutions given. A deeper analysis of both formulations must be presented. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I would appreciate your comments to enhance and clarify this section of the paper.

The problem (13) is feasible and has feasibility points discussed in Subsection IV-B, and we introduce a fast algorithm (i.e., Algorithm 3 in Subsection IV-B) for feasibility points. Although the problem is feasible, it is not convex and challenging to solve. Since problem (13) is mixed-integer nonlinear programming with two integer variables, the PRB assignment, $e$, and the number of VNFs in slice $s$, $M_s$, and by relaxing the variables, the problem is also non-convex; therefore, this problem is NP-hard. Solving the problem is not trivial. To solve the problem by inspiring Stackelberg, we reformulate the equation in (13g) to reduce one of the variables (i.e., $M_s$) that can be solved after obtaining the rate of UEs. We notice that $M_s$ is similar to the followers in Stackelberg Competition, and power and PRB assignment are identical to the leader. So, the new problem has two variables: power and PRB assignment. This new problem is convex by relaxing the binary variable, the PRB assignment, and estimating the lower bounds (15). The objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs in each slice ($M_s$). We made changes in Subsection III-A, accordingly.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``Moreover, the baseline and FBDR methods used in the comparison are not well introduced. They are vaguely linked to related work but not as needed. The paper must clarify the relation of the related work and the compared alternatives. The paper must also contextualize the proposal among the related work by comparing their qualities and/or performance.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for emphasizing this point and helping us with a better exhibition.

 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach.

 The first one is a baseline scheme, which uses random PRB allocation. Therefore, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE. Also, the association of O-RU is carried out based on distance. It means that each UE is assigned to the nearest O-RU. The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex.
After achieving power and other parameters, the achievable rate will be obtained, and the optimal number of VNF is achieved from Lemma (1).

For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme). 
 We have services with different QoS in this work, similar to tenants with different QoS introduced in [18]. Therefore, we can use the DR scheme similar to the FBDR method adapted to our conditions for comparison. Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
 Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
But also, we can assume that O-DU and O-CU have fixed sufficient capacity in our system model. Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the idea of the FBDR method with this assumption and using the DR scheme. In the DR scheme, PRB and power are dynamically allocated. The number of VNFs is obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm) for O-RU assignment. The figures in [18] show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area. The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.

@@

\\
\hline
\end{longtable}

In [1 page 11], the amount of BW is explained. In [2], the noise power is represented. The amount of delay for eMBB and URLLC are listed on Pages 24 and 25 in [5]. Also, on Page 26, the mMTC packet size is stated. On Page 25, the URLLC packet size is stated.
In [3], on Page 13, Table 6.1, the maximum power is stated. In [4], on Page 4, the delay of URLLC and eMBB is and also the spectral efficiency of eMBB is noted.

We add these references in IV-A (references [41]-[45]).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 2} \\
\hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author:} ``The paper focus on the aspect of network slicing in 5G cellular network which entails a service aware resource allocation of the different required virtual network functions (VNFs) for different slices which have different characteristics. More specifically, the paper proposes a mixed integer mathematical problem which in the original form is non-linear and hence hard to solve. To tackle this challenge the optimization problem is decomposed into two sub-problems where the solutions are not optimal however numerical investigations show that the solutions are competitive. In general, the paper is well written and structured.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing thoughtful comments, and offering constructive suggestions that strengthened and enhanced its quality. We hope that the responses provided herein can alleviate the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``In terms of taking the actual delay in the proposed there are some concerns which might be important for some time critical applications especially in the ultra-reliable low latency communications (URLLC) but also for different applications that fall under the enhanced mobile broadband (eMBB) generic service framework. First of all, in the paper the authors only consider processing delay and ignore propagation and transmission delay. Since multiple paths in reality could be utilized the role of the above two components might play an important role. Nevertheless, the authors need to clearly mention why those two components are not considered, saying for example are constant is not a good enough reason to be ignored since as eluded those change based on routing decisions.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for this comment to add more detail to our paper regarding end-to-end delays.

Taking propagation and transmission delays into formulations is straightforward, but we avoided that for the sake of better presentation. However, they can be added to the system model easily. In this paper, we focus only on the processing delay to find the optimal number of VNFs, and we consider the other two delays are fixed. We discuss these two types of delay in detail below and explain why we do not consider them in our work.

The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority. Also, the connections of O-DUs to O-CUs are the same as O-RU to O-DU. Therefore, different routes will be added to the system to solve the routing problem. Also, for URLLC and mMTC, edge processing can reduce the delay that is not considered here.
However, it provides a new problem formulation and can be added to our system model to extend our paper in the future. Thus, this paper assumes that the connection between O-RUs and O-DUs is fixed and transparent, and we do not consider the problem of edge processing. As a result, the propagation delay is fixed and does not affect the optimization problem. The following is a brief calculation of propagation and transmission delay.
Since the distance between the O-RU and O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km. Moreover, the distance from O-CU to the network should not exceed 200 Km [35]. so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $. Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light. Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced. But we also do not focus on edge processing in this paper. You can find more about these distances in this \href{https://blogs.keysight.com/blogs/inds.entry.html/2020/06/30/5g_testing_what_is-0nzj.html\%23:~:text=The\%20data\%20requirements\%20are\%20about,DUs\%20is\%20about\%2080\%20km.}{link}.

The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has a small amount.
In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 \frac{bit}{\frac{sec}{Hz}} \times BW (180 KHz)$. So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$. As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$. for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.

@@

We add this response in subsection II-D.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Also, note that for calculating processing delay requests for different services arriving at blade servers for vnf applications might get different treatment on how they access VMs or containers hence a single queue with non-priority and/or preemption (m/m/1) might not be a good approximation on the performance.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
The processing delay can be modeled as an M/M/1 queue; since the system's arrival packets are from many independent sources. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. The system's clock is constant, and the size of the tasks is not fixed. So, we suppose that service times are exponentially distributed [36]. In addition, we assume that the arrival packets of each service have the same priority (in subsection II-F, we will talk about priority), and we consider priority between services, not between UEs of one service. As we assume that the UEs of a service have the same priority, their sent packets also have an equal priority. In addition, since the services are isolated, the UEs in each service have the same priority, and the processing delays of each service are independent of the other services; if we assume service priority, this priority does not invalidate the queueing theory. Therefore, one service could have a higher priority, affecting the whole optimization, and the M/M/1 queue theory is still validated.

@@

We add this response in subsection II-D-1.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 3:} ``Also worth noting, that later on in the problem formulation there is the notion of service priority $\delta_s$ for data rate but this seems not to be used for accessing cloud resources. For example one could have changed the optimization problem and considered average allocated transmission rate and optimize with the same priorities access to cloud resources (instead of allocating equal access to vnf resources).''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the great suggestion they gave us.
Since the priority is in the objective function of the equation (13), the priority has affected the whole optimization problem.
Therefore, priority is given to the whole optimization problem, and the optimization problem obtains the number of VNFs by affecting the priority term. If we were to discuss the placement of VNFs on the data centers, the problem would become a knapsack or bin-packing problem, and here the prioritization would affect the resource allocation algorithm, including memory, RAM, CPU, and bandwidth of VNFs. Therefore, the algorithm was implemented based on prioritization. But, in this paper, we consider priority more generally. This is an excellent suggestion for extending this paper in the future. Hence, in the extension of the paper, we would talk about VNF placement, and the priority will be more different from here, and the access of VNF resources will be based on the priority.

@@

\\
\hline
\end{longtable}

On [1, Page 25], the URLLC packet size is stated to be 32 bytes, and on Page 26, the packet size of mMTC is stated to be 20 bytes. We changed the URLLC packet size to 32, but it has little impact on the simulation result.

We add this reference in IV-A (reference [45]).

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 7:} ``Comparison with [18] might not be fair since that work also considers BBU capacity and also performs admission control functionalities, also there are different tenants that have different users with variable required QoS. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We appreciate the reviewer emphasizing this point and providing us with tips on how to improve our paper.

For the second one, we use the idea of the fixed BBU capacity and dynamic resource allocation (FBDR) algorithm proposed in [18] and named it the dynamic resource allocation scheme (DR scheme). 
 We have services with different QoS in this work, similar to tenants with different QoS introduced in [18]. Therefore, we can use the DR scheme similar to the FBDR method adapted to our conditions for comparison. Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
 Since we do not talk about O-DU and O-CU capacity, we use the dynamic resource allocation scheme (DR scheme) algorithm and do not consider BBU capacity.
But also, we can assume that O-DU and O-CU have fixed sufficient capacity in our system model. Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the idea of the FBDR method with this assumption and using the DR scheme. In the DR scheme, PRB and power are dynamically allocated. The number of VNFs is obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the channel distance instead of using the greedy algorithm 1 (GAA algorithm) for O-RU assignment. The figures in [18] show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same priority area. The numerical results section also indicates that our proposed algorithm performs better than the DR scheme.

@@

We add this response in subsection IV-A.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 8:} ``Also, interference is measured in a more detailed manner (maximum interference per UE) and hence when this relaxed (Guassian noise) the performance expected to slightly increase. Hence, some more detailed discussion on what has been assumed is needed. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Here we have two Gaussian noise types: additive Gaussian noise and the other is Gaussian quantization noise which is shown in Fig \ref{fig:pq}. We offer the sum of interference and the Gaussian quantization noise with $ I_{r,u(s,i)}^{k}$. Also, the Gaussian quantization noise is independent of interference and related to channel gain of UEs.

We add this response in subsection II-B.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-03-22 Journal1/paper4TNSM/pr.tex
add sth:

Taking advantage of virtual radio access network (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility, openness, reduces operational costs, and agile deployment. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).

@@

\textcolor{blue}{To achieve the desired level of QoS (quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks. There are several implementations of network slicing, including core slicing, RAN slicing, and both. 
Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on QoS, each service requires its own slice of the network.
The eMBB service fulfills the demand for high capacity and throughput. The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency. mMTC is comprised of many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring

@@

\textcolor{OrangeRed}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed as a result of integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

@@

\textcolor{blue}{In order to achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
The purpose of this study is to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follows:

@@

\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end processing delay of the system based on the number of activated VNFs and user throughput.
Assuming a limited fronthaul capacity, we calculate the power and capacity of each O-RU. We model the interference of neighboring O-RUs and formulate the actual throughput for different service types. Based on the short packet transmission of URLLC and mMTC, we also model their throughput.

@@

  \caption{Network sliced ORAN system}

@@

In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.

@@

There are three service types including eMBB, URLLC, and mMTC which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the eMBB, URLLC, and mMTC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node

There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have 
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system. Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

%All $K$ PRBs can be assigned to all UEs in each service. 
\textcolor{Sepia}{ Assume we have $K$ physical resource blocks (PRBs) in this system. Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.
}
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

>>>>

Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. Due to O-RAN, flexibility, openness, and lower operational costs will be possible. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).

@@

\textcolor{MidnightBlue}{To achieve the desired level of QoS (i.e., quality, delay, power, etc.) and isolate different services, network slicing is the most effective solution for 5G wireless cellular networks. There are diferent implementations of network slicing, including core slicing, RAN slicing, and both.
Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on QoS, each service requires its slice of the network.
The eMBB service fulfills the demand for high capacity and throughput. The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency. mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads 

@@

\textcolor{MidnightBlue}{This paper considers a number of user equipments (UEs) requesting one of these types of services with different QoS. We would like to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{MidnightBlue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (CRAN). With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

\textcolor{MidnightBlue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}

\textcolor{MidnightBlue}{This paper aims to design a RAN slicing technology for the O-RAN architecture. }
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{MidnightBlue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
\textcolor{MidnightBlue}{The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing. We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}

In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:

@@

\item \textcolor{MidnightBlue}{This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC. Within the O-RAN architecture, the problem of radio resource allocation and VNF activation is explored.
Based on different types of services with different QoS and service priorities, we formulate a problem for the allocation of baseband resources to maximize the weighted throughput of O-RAN.}
\item \textcolor{MidnightBlue}{We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers. Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture. }
\item \textcolor{MidnightBlue}{Different services need to consider varying QoS conditions, including delay, power, and throughput. According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.
Assuming a limited fronthaul capacity, we calculate each O-RU's actual power and capacity. Depending on the service type, we model the interference of neighboring O-RUs and determine the actual throughput. Our model accounts for the short packet transmission of URLLC, and mMTC, which cannot be modeled by the Shannon capacity theorem.}

@@

  \caption{Network sliced o-ran system}

@@

In this section, we describe the downlink system in the O-RAN architecture using RAN slicing as depicted in Figure \ref{fig:c11}.
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system. Afterward, we discuss the mean delay and the power of VNFs.

@@

Assume, there are three service types including eMBB, URLLC, and mMTC which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S$ pre-allocated slices serving these $S$ services ($S = S_1 + S_2 + S_3$);
Hence, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.

Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}
Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system. Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

%All $K$ PRBs can be assigned to all UEs in each service.
\textcolor{MidnightBlue}{ Assume there are $K$ physical resource blocks (PRBs) in this system. Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.
}
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.
